Incorporating periodic variability in hidden Markov models for animal movement

### 2016-07-12 paper3.Rnw
ggalt tweaking

\doublespacing
<<pkgs,message=FALSE,warning=FALSE,echo=FALSE>>=
library("ggplot2"); theme_set(theme_bw())
scale_colour_discrete <- function(...,palette="Set1")
    scale_colour_brewer(...,palette=palette)
scale_fill_discrete <- function(...,palette="Set1")
    scale_fill_brewer(...,palette=palette)
zmargin <- theme(panel.margin=grid::unit(0,"lines"))
library("knitr")
opts_chunk$set(fig.width=6,fig.height=4)
## fix complaints about "incompatible color definition" from xcolor ...
## http://tex.stackexchange.com/questions/148188/knitr-xcolor-incompatible-color-definition
knit_hooks$set(document = function(x) {sub('\\usepackage[]{color}', '\\usepackage{xcolor}', x, fixed = TRUE)})
library("depmixS4")
library("plyr")
library("dplyr")
library("reshape2")
library("gridExtra")
library("RColorBrewer")
# if (!require("ggalt")) {
#     cat("installing ggalt from BB repo ...\n")
#     library("devtools")
#     install_github("bbolker/ggalt")
#     library("ggalt")
# }
library("ggalt")
@

>>>>

\doublespacing
<<pkgs,message=FALSE,warning=FALSE,echo=FALSE>>=
library("ggplot2"); theme_set(theme_bw())
scale_colour_discrete <- function(...,palette="Set1")
    scale_colour_brewer(...,palette=palette)
scale_fill_discrete <- function(...,palette="Set1")
    scale_fill_brewer(...,palette=palette)
zmargin <- theme(panel.margin=grid::unit(0,"lines"))
library("knitr")
opts_chunk$set(fig.width=6,fig.height=4)
## fix complaints about "incompatible color definition" from xcolor ...
## http://tex.stackexchange.com/questions/148188/knitr-xcolor-incompatible-color-definition
knit_hooks$set(document = function(x) {sub('\\usepackage[]{color}', '\\usepackage{xcolor}', x, fixed = TRUE)})
library("depmixS4")
library("plyr")
library("dplyr")
library("reshape2")
library("gridExtra")
library("RColorBrewer")
if (!require("ggalt") || length(find("geom_encircle"))==0) {
#     cat("installing ggalt from BB repo ...\n")
    try(detach("package:ggalt"),silent=TRUE)
    devtools::install_github("hrbrmstr/ggalt")
    library("ggalt")
}
@
